---
title: "PUBLIC HEALTH WHOLE GENOME SEQUENCING ANALYSIS REPORT"
output:
  officedown::rdocx_document:
    tables:
      align: center
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    plots:
      style: Normal
      align: center
      caption:
        style: Image Caption
        pre: 'Figure '
        sep: ': '
    lists:
      ol.style: null
      ul.style: null
    mapstyles:
      Normal: ['First Paragraph', 'Author', 'Date']
    page_size:
      width: 8.5
      height: 11
      orient: "portrait"
    page_margins:
      bottom: 1
      top: 1
      right: 0.75
      left: 0.75
      header: 0.01
      footer: 0.01
      gutter: 0.01
    reference_num: true
---

```{r setup, include=FALSE}

#if (!requireNamespace("BiocManager", quietly = TRUE))
#  install.packages("BiocManager")
#BiocManager::install("ggtree")

library(officedown)
library(officer)
library(flextable)
library(ggplot2)
library(plotly)
library(ape)
library(ggtree)
library(heatmaply)
library(phytools)
library(flextable)
library(dplyr)
library(tidyverse)
library(huxtable)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE)
set_flextable_defaults(font.family = 'Arial')
text_format <- fp_text(font.size = 12, font.family = "Arial")

```

`r ftext(subHeaderText,prop = text_format)`

```{r intro}

# create table
colnames(headerDF) <- c("REPORT DATE","PROJECT NAME","PREPARED BY")

# plot table
ft <- flextable(headerDF)
ft %>% autofit(part = "all") %>% fit_to_width(8)
# %>% padding(padding = 1, part = "all")
```

# SUMMARY

`r ftext(summaryTEXT,prop = text_format)`

\newpage

# SAMPLES

```{r samples}

# create table
colnames(sampleDF) <- c("Lab ID", "Isolate Collection Date", "Local ID", "Species ID", "Specimen Source","MLST", "Resistance Genes", "Comments","TreeGroup")

# plot table
#ft <- flextable(sampleDF) %>% set_table_properties(layout = "autofit")
#ftt <- FitFlextableToPage(ft)
#ft
#ft %>% autofit(part = "all") %>% fit_to_width(8)
sample_ht <- as_hux(sampleDF)

sample_ht <- sample_ht %>%
      set_all_padding(1) %>%
#      set_outer_padding(0) %>%
      set_number_format(0) %>%
      set_bold(row = 1, col = everywhere) %>%
#      set_bottom_border(row = 2, col = everywhere) %>%
#      set_width(1) %>%
      set_background_color(evens, everywhere, "grey95")

ft <- as_flextable(sample_ht)
ft %>% autofit(part = "all") %>% fit_to_width(7)

```


\newpage


`r if(exists('snpData') | exists('treepath')){"# RELATEDNESS"}`

`r if(exists('snpData')){"## HEATMAP"}`

`r if(exists('snpData')){ftext(config$heatmap.text,prop = text_format)}`

```{r heatmap, fig.width=7, fig.height=5}
if(exists('snpData') && config$show.snp==TRUE){
  rownames(snpData) <- snpData$X
  snpData <- snpData [,-1]
  fig <- heatmaply(snpData,
            cellnote=snpData,
            colors = viridis(n = 256, alpha = 1, begin = 1, end = 0, option = "viridis"),
            show_dendrogram = c(FALSE, FALSE), plot_method = "plotly",
            dist_method=config$heat.dist.method, label_names = c("Row", "Column", "SNPs"))
  orca(fig, "snp-plot.png", width = 7 * 96, height = 5 * 96)
  fpar_fig <- fpar(external_img(src = "snp-plot.png", height = 5, width = 7))
  fpar_fig
}

if(exists('snpData') && config$show.snp==FALSE){
  rownames(snpData) <- snpData$X
  snpData <- snpData [,-1]
  fig <- heatmaply(snpData,
            colors = viridis(n = 256, alpha = 1, begin = 1, end = 0, option = "viridis"),
            show_dendrogram = c(FALSE, FALSE),
            dist_method=config$heat.dist.method, plot_method = "plotly")
  orca(fig, "snp-plot.png", width = 7 * 96, height = 5 * 96)
  fpar_fig <- fpar(external_img(src = "snp-plot.png", height = 5, width = 7))
  fpar_fig
}

```


\newpage


`r if(exists('treepath')){"## PHYLOGENETIC TREE"}`

`r if(exists('treepath')){ftext(config$tree.text,prop = text_format)}`

`r if(exists('treepath') & exists('cgstats')){ftext(paste("Core Genes Identified: ",cgstats[cgstats$V1 == 'Core genes',3],'\n'),prop = text_format)}`

`r if(exists('treepath') & exists('cgstats')){ftext(paste("Total Genes Identified: ",cgstats[cgstats$V1 == 'Total genes',3]),prop = text_format)}`

```{r tree, message=FALSE}
if(exists('treepath')){
  set.seed(42)
  tree <- ape::read.tree(treepath)

  if(exists('cgstats')){
    paste("Core Genes Identified: ",cgstats[cgstats$V1 == 'Core genes',3])
    paste("Total Genes Identified: ",cgstats[cgstats$V1 == 'Total genes',3])
  }

  if(config$root.method == 'midpoint'){
    tree <- midpoint.root(tree)
  }
  else if(config$root.method == 'unrooted'){
    tree <- tree
  }
  else {
    node <- match(config$root.method, tree$tip.label)
    if(is.na(node)){
      message('Root sample ID not found')
      quit(save="no", status=1)
    } else {
      tree <- reroot(tree,node)
    }
  }

  # metadata
  id <- tree$tip.label

  # group samples if we have a grouping catagory
  if(any(!is.na(sampleDF$TreeGroup))){
    #reorder sampleDF
    orderedDF <- sampleDF[match(id,sampleDF$'Lab ID'),]
    grp <- orderedDF$TreeGroup
  }
  else {
    grp <- NULL
  }

  dat <- tibble::tibble(id = id)
  # plot tree
  ggtree_plot <- ggtree(tree)
  metat <- ggtree_plot$data %>%
    dplyr::inner_join(dat, c('label' = 'id'))

  ggtree_plot <- ggtree_plot +
    geom_point(data = metat,
               aes(x = x,
                   y = y,
                   colour = grp,
                   label = id, text = paste0(id)),show.legend = FALSE)

  d <- ggtree_plot$data

  if(config$show.bootstrap){
    #filter bootstrap values
    d <- ggtree_plot$data
    bs <- d[!d$isTip,]
    bs$label <- as.numeric(bs$label)
    bs <- bs[bs$label > bootstrap.threshold,]
    ggtree_plot <- ggtree_plot + geom_text(data=bs,aes(label=label), nudge_x = -0.0001)
  }

  tl <- d[d$isTip,]
  ggtree_plot <- ggtree_plot + geom_text(data=tl,aes(label=label), nudge_x = 0.00015)

  fig <- ggplotly(ggtree_plot, tooltip = "text")
  orca(fig, "tree-plot.png", width = 6.5 * 72, height = 6.5 * 72)
  fpar_fig <- fpar(external_img(src = "tree-plot.png", height = 6.5, width = 6.5))
  fpar_fig
}
```

\newpage


`r if(exists('ar_summary')){"# AR GENE SUMMARY"}`

`r if(exists('ar_summary')){ftext(config$ar_gene_summary.text,prop = text_format)}`


```{r ar_table}
if(exists('ar_summary')){
  ar_summary <- ar_summary[order(ar_summary$Sample),]
  row.names(ar_summary) <- NULL

  ar_ht <- as_hux(ar_summary)
  ar_ht <- ar_ht %>%
      set_all_padding(1) %>%
      set_number_format(0) %>%
      set_bold(row = 1, col = everywhere) %>%
      set_background_color(evens, everywhere, "grey95")

  ft <- as_flextable(ar_ht)
  ft %>% autofit(part = "all") %>% fit_to_width(7)
}
```

\newpage

`r if(exists('optionalData')){"# ADDITIONAL ANALYSES"}`
`r if(exists('optionalData')){ftext(config$optionaldata.text,prop = text_format)}`

```{r additional tables, results='asis'}

if(exists('optionalData')){
  count <- 0
  for(i in 1:length(optionalData)){
    count <- count + 1
    df <- optionalData[[i]]

    df_ht <- as_hux(df)
    df_ht <- df_ht %>%
      set_all_padding(1) %>%
      set_number_format(0) %>%
      set_bold(row = 1, col = everywhere) %>%
      set_background_color(evens, everywhere, "grey95")

    cat("<w:p/>")
    ft <- as_flextable(df_ht)
    ft <- ft %>% autofit(part = "all") %>% fit_to_width(7)
    flextable_to_rmd(ft)
  }
}
```

# METHODS
`r ftext(methodsTEXT,prop = text_format)`

\newpage

# DISCLAIMER
`r ftext(disclaimerTEXT,prop = text_format)`
